\noindent \textbf{\textcolor{bluename}{\Large Steven L. Harville}} \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ www.steven-harville.com
\\

\hfill 607 SE 18th Ave.

\hfill Portland, OR  97214

\hfill (503) 891.3306

\noindent May 13, 2011\\%																													...REMEMBER TO CHANGE ME!

%\noindent \textbf{Recipient Name}\\%																										...REMEMBER TO CHANGE ME!
%\noindent Address line 1\\%																													...REMEMBER TO CHANGE ME!
%\noindent Address line 2\\%																													...REMEMBER TO CHANGE ME!
%\noindent City, State/Province  Zip\\%																									...REMEMBER TO CHANGE ME!

\noindent Dear Sir/Madam,
\\

% State the position and intent
\noindent This is in reference to the position for a Meteorologist advertised on your website. I am very interested in this position and believe that I have the relevant education and employment background.
\\

% General education, experience with specific examples
\noindent I have a BS and MS (with dissertation) in Meteorology from North Carolina State University. I have a strong background in theoretical and operational aspects of weather forecasting. I am very proficient in statistical, computing, and numerical methods. I have extensive experience in programming and scripting languages (e.g., Fortran, Python, Perl, JavaScript, HTML, LaTeX, csh) and in running complex numerical weather prediction models (Weather Research and Forecasting - WRF model). I am also comfortable with a variety of operating systems (UNIX/Linux, Mac OS, Windows) and analysis and visualization software (GEMPAK, GrADS, ArcGIS).
\\

% Mention individual projects (co.cc), the trend towards more independently worked projects of greater technical complexity, creating your own professional internships (Adapt)
\noindent 
%Though a classically trained meteorologist, my interests and strengths have always swayed toward the more technical side of the discipline. As a graduate research assistant, I gained on-the-job experience working with our in-house Linux server. Since graduating, my work has purposefully stepped further into the field of computer science. I have contracted myself out this past year as a web developer and freelance programmer and have volunteered time developing customized educational software for children with autism. The knowledge gained from these experiences has allowed me to pursue projects of perpetually increasing technical complexity.
\\

% Wrap it up
\noindent Please find attached my resume, which documents my educational and professional experience. I look forward to hearing from you.
\\

\noindent Thank you for your consideration.
\\

\tab{Sincerely,}
\\

\tab{Steven Harville}
